Iroko: Predictive Datacenter Congestion Control

### 2017-12-10 Documents/Report/intro.tex
More intro writing.

\paragraph{Predictability of traffic}
Remy\cite{remy} has shown that it is possible to learn optimal congestion 
control parameters for various network topologies, but 
Due the scarcity of public data center traffic sets, it is unclear how 
predictable traffic truly is.

>>>>

\paragraph{Predictability of traffic}
Although it is unclear how predictable data center traffic truly is, various 
works have shown that repeated patterns may 
exist.\cite{msr_dc,fb_dc,traffic,microte}
If data center traffic exhibits predictable patterns over long time, it may be 
possible to devise a proactive mechanism which predicts the traffic matrix of 
the next nth iterations, and adjusts traffic accordingly.

%Winstein and Balakrishnan,~2013\cite{remy} demonstrated that it is possible to 
%learn optimal TCP congestion control parameters for various network 
%topologies. 
%Benson et al.,~2014\cite{microte} analyzed data center traffic and inferred 
%that around 30\%
